NIRCam Faint and Bright Flux Calibration Plan

### 2018-04-20 ms.tex
added a few notes about the flux ladder & APT templates.

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band. This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.15 mag.
Thus, to calibrate all wide band filters in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module).
We selected clusters with WEBDA diameters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
\end{itemize}

@@

\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}

@@

\subsubsection{Implementation}
The APT science nor engineering template permit dithered subarray imaging with a 64$\times$64 subarray through a neutral density filter.
This prohibits executing Step 1 in Cycle 1 observing.
It is possible that in Cycle 2, more modes will be implemented including dithered subarray 64$\times$64 subarray imaging with a neutral density filter in place.

>>>>

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band. This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.15 mag.
Thus, to calibrate all wide band filters longer than F200W in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module).
We selected clusters with WEBDA diameters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
\end{itemize}

@@

\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder\footnote{This idea has been discussed, but cannot be executed until Cycle 2 due to limitations of observing templates}}

@@

\subsubsection{Implementation}\label{sec:ImpIssue}
The APT science nor engineering template permit dithered subarray imaging with a 64$\times$64 subarray through a neutral density filter.
This prohibits executing Step 1 in Cycle 1 observing.
It is possible that in Cycle 2, more modes will be implemented including dithered subarray 64$\times$64 subarray imaging with a neutral density filter in place.
